### 2019-02-28 manuscript/results.tex
- pathway figure legend mods

% E todo: could make this look a little less klunky
\begin{figure}
    \centering \includegraphics[width=0.9\textwidth]{pathways}
    \caption{
        Contributions of the two pathways to polyploidy.
        When considering only rates of transitions among the states (left), the one-step pathway dominates on short timescales and the two-step on long timescales.
        When also considering diversification within each state (right), the one-step pathway dominates over any timescale.
        The lower panels plot the ratio of the two pathway contributions in the upper panels.
    }
    \label{figure:pathways}
\end{figure}

>>>>

% E todo: could make this look a little less klunky
\begin{figure}
    \centering \includegraphics[width=0.9\textwidth]{pathways}
    \caption{
        %B: FIXME: R&E check this re-wording to see if it is to your liking--I think I clarified it a bit, although with length increase.
        %Contributions of the two pathways to polyploidy.
        %When considering only rates of transitions among the states (left), the one-step pathway dominates on short timescales and the two-step on long timescales.
        %When also considering diversification within each state (right), the one-step pathway dominates over any timescale.
        %The lower panels plot the ratio of the two pathway contributions in the upper panels.
        Contributions of the two pathways to polyploidy, the one-step ID$\rightarrow$CP transitions, and the two-step, ID$\rightarrow$CD$\rightarrow$CP transitions.
        Panel (a) shows the contributions when considering only transition rates among the states (ignoring the diversification rate parameters). 
        The one-step pathway dominates on short timescales and the two-step on long timescales.
        Panels (b) shows the contributions when including diversification of lineages in each state. 
        The one-step pathway, in which polyploidy breaks down SI, dominates over any timescale.
        Panels (c) and (d) plot the ratio of the pathway contributions in the upper panels, (a) and (b), respectively.
    }

    the one-step pathway, from ID to CP

    \label{figure:pathways}
\end{figure}
